---
title: "I-CONECT DSMB Report"
# author: "Nicolas May"
# date: "2/25/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

<!-- Load packages. -->

```{r packages}
library(dplyr)
library(stringr)
library(knitr)
library(kableExtra)
```

<!-- Load custom functions. -->

```{r}
prettify_table <- function(x) {
  x %>%
    kable(format = "pandoc")
}
```


<!-- Load data. -->

```{r}
df_ic_raw <-
  data.table::fread(
    "./OCTRI5793Internetbas_DATA_2019-02-25_1116.csv"
  ) %>% 
  na_if("")

df_ic <- 
  data.table::fread(
    "./OCTRI5793Internetbas_DATA_LABELS_2019-02-25_1146.csv"
  ) %>% 
  na_if("")

names(df_ic) <- names(df_ic_raw)
```


# Study Administration Recruitment and Participant Status

```{r}
# Get relevant fields
df_ic_status <- df_ic %>% 
  # select relevant field(s)
  select(
    ts_sub_id
    , redcap_event_name
    , redcap_repeat_instrument
    , redcap_repeat_instance
    , ps_stt # 1 In Scrn, 2 Scrn Fail, 3 Enrld, 4 Act, 5 In flwup, 6 Dicont
    , ps_scr 
    , ps_fal
  )

```

```{r}
# Clean data
df_ic_status_cln <- df_ic_status %>% 
  # keep only pt. IDs
  filter(str_detect(ts_sub_id, "^C\\d{4}$")) %>% 
  # filter relevant arm(s)
  filter(redcap_event_name == "Admin") %>% 
  # keep only pts. with "current participant status" (ps_stt)
  filter(!is.na(ps_stt)) %>%
  # keep only pts. with "consent date" (ps_scr)
  filter(!is.na(ps_scr)) %>% 
  # keep only pts. WITHOUT "failure date" (ps_fal)
  filter(is.na(ps_fal))
```

```{r}
# Mutate data
df_ic_status_cln_mut <- df_ic_status_cln %>% 
  # Coerce `ps_scr` to date
  mutate(ps_scr = lubridate::mdy(ps_scr)) %>% 
  # ID integer
  mutate(ts_sub_id_int = 
           as.integer(str_extract(ts_sub_id, pattern = "\\d{4}"))) %>% 
  # OHSU / UM label
  mutate(site = case_when(
    between(ts_sub_id_int, 1001, 1999) ~ "OHSU",
    between(ts_sub_id_int, 2001, 2999) ~ "UM",
    TRUE ~ NA_character_
  )) %>% 
  # Arrange by ts_sub_id, ps_scr  
  arrange(ts_sub_id, ps_scr)
```

**Figure 2a-c: Overall Study Status**

**Figure 3a-c Enrollment: Actual vs. Expected**

**Table 1: Site Enrollment by Period**

**Table 2: Partcipant Enrollment Status**

```{r table2}
df_ic_status_cln_mut %>% 
  group_by(ps_stt) %>% 
  summarize(n = n()) %>% 
  prettify_table()
```

**Table 3a-b: Participant Enrollment Status by Site**

```{r table3a}
df_ic_status_cln_mut %>% 
  filter(site == "OHSU") %>% 
  group_by(ps_stt) %>% 
  summarize(n = n()) %>% 
  prettify_table()
```

```{r table3b}
df_ic_status_cln_mut %>% 
  filter(site == "UM") %>% 
  group_by(ps_stt) %>% 
  summarize(n = n()) %>% 
  prettify_table()
```

```{r table3c}

```

**Table 4: Reasons for Screen Failures (Cumulative*)**

```{r table4}

```

**Table 5: Main Trial Protocol Deviations**

```{r table5}

```

**Table 6: Main Trial Protocol Deviations by Classification**

```{r table6}

```

**Table 7a-b: Main Trial Protocol Deviations by Site**

```{r table7a}

```

```{r table7b}

```

```{r table7c}

```

**Table 8: Main Trial Demographic and Key Baseline Characteristics**

```{r}
# Get relevant fields
df_ic_demodx <- df_ic %>% 
  # select relevant fields
  select(
    ts_sub_id
    , redcap_event_name
    , redcap_repeat_instrument
    , nac_sex
    , nac_hispanic
    , nac_race
    , nac_a1_age
    , nac_normcog
    , nac_mciamem
    , nac_mciaplus
    , nac_mcinon1
    , nac_mcinon2
  )
```

```{r}
# Clean data
df_ic_demo_cln <- df_ic_demodx %>% 
  # keep only pt. IDs
  filter(str_detect(ts_sub_id, "^C\\d{4}$")) %>% 
  # filter relevant arm(s)
  filter(redcap_event_name == "Scrn V") %>% 
  # filter relevant repeat instruments
  filter(redcap_repeat_instrument == "Demographics (NACC A1)")

df_ic_dx_cln <- df_ic_demodx %>% 
  # keep only pt. IDs
  filter(str_detect(ts_sub_id, "^C\\d{4}$")) %>%
  # filter relevant arms
  filter(redcap_event_name == "BL CDx") %>% 
  # filter relevant repeat instruments
  filter(redcap_repeat_instrument == "Clinician Diagnosis (NACC D1)")
```

```{r}
# Summarize data
df_ic_demo_cln %>% 
  group_by(nac_sex) %>% 
  summarize(n = n()) %>% 
  prettify_table()

df_ic_demo_cln %>% 
  group_by(nac_hispanic) %>% 
  summarize(n = n()) %>% 
  prettify_table()

df_ic_demo_cln %>% 
  group_by(nac_race) %>% 
  summarize(n = n()) %>% 
  prettify_table()

df_ic_demo_cln %>% 
  summarize(Age_Mean = mean(nac_a1_age, na.rm = TRUE),
            Age_Median = median(nac_a1_age, na.rm = TRUE),
            Age_SD = sd(nac_a1_age, na.rm = TRUE),
            Age_Min = min(nac_a1_age, na.rm = TRUE),
            Age_Max = max(nac_a1_age, na.rm = TRUE)) %>% 
  prettify_table()
```




